Meta-analysis for the Effect of SSRIs on Anxiety

### 2023-02-20 codebook_dat.Rmd
add multiplier

---
title: "Codebook created on 2023-01-01 at 2023-01-01 17:14:20"
output: github_document
---

@@

## Dataset description
The data contains 20 cases and 24 variables.

>>>>

---
title: "Codebook created on 2023-02-20 at 2023-02-20 10:30:46"
output: github_document
---

@@

## Dataset description
The data contains 465 cases and 21 variables.

### 2023-02-20 manuscript/manuscript.Rmd
add multiplier

dat <- dat[!is.na(dat$yi), ]

zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
#if(maxz > 3.3) stop("Potential outlier in Y-space")
#dat <- dat[!abs(zscores) > 3.3, ]
saveRDS(dat, "dat.RData")
```

>>>>

dat <- dat[!is.na(dat$yi), ]
dat$yi <- dat$yi * dat$multiplier
dat[["multiplier"]] <- NULL
zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
#if(maxz > 3.3) stop("Potential outlier in Y-space")
dat <- dat[!abs(zscores) > 3.3, ]
saveRDS(dat, "dat.RData")
```
